\begin{thebibliography}{9}
 
\bibitem{aclsuse}
  Andreas Gruenbacher,
  \emph{POSIX Acess Control Lists on Linux}.
  http://www.suse.de/~agruen/acl/linux-acls/online/,
  2003.

\bibitem{ieee1}
    IEEE Std 1003.1-2001 (Open Group Technical Standard, Issue 6), 
	Standard for Information Technology--Portable Operating System Interface (POSIX) 2001. 
	ISBN 0-7381-3010-9. 
	http://www.ieee.org/

\bibitem{ieee2}
    IEEE 1003.1e and 1003.2c: Draft Standard for Information Technology--Portable Operating System Interface (POSIX)--Part 1: System Application Program Interface (API) and Part 2: Shell and Utilities, draft 17 (withdrawn). 
	October 1997. 
	http://wt.xpilot.org/publications/posix.1e/

\bibitem{ftp}
	Mark Lowes: 
	Proftpd: 
	A User's Guide March 31, 2003. 
	http://proftpd.linux.co.uk/

\bibitem{posix17}
    Winfried Trümper: Summary about Posix.1e. Publicly available copies of POSIX 1003.1e/1003.2c. February 28, 1999. http://wt.xpilot.org/publications/posix.1e/

\bibitem{acl_permission}
	Jim Mauro: Controlling permissions with ACLs. Describes internals of UFS's shadow inode concept. SunWorld Online, June 1998.

\bibitem{trust}
	Robert N. M. Watson: Introducing Supporting Infrastructure for Trusted Operating System Support in FreeBSD. BSDCon 2000, Monterey, CA, September 8, 2000. http://www.trustedbsd.org/docs.html
	
\bibitem{nfs_problem}
	Andreas Grünbacher: Linux Extended Attributes and ACLs. Session "Known Problems and Bugs". http://acl.bestbits.at/problems.html
	
\bibitem{ext_acl}
	Andreas Dilger: [RFC] new design for EA on- disk format. Mailing list communication, July 10, 2002. http://acl.bestbits.at/pipermail/acl-devel/ 2002-July/001077.html

\end{thebibliography}
